Dependent Object Types

### 2012-07-01 doc/semester/report.tex
program excerpts

% TODO

>>>>

\subsection{Program Examples}

\begin{align*}
&\mlnew {\mi{root}} {\Top \mlrefine r {\\
&\ \Ldecl {\mi{Unit}} \Bot \Top\\
&\ \ldecl {\mi{unit}} {\Top \tfun {r.\mi{Unit}}}\\
&\ \Ldecl {\mi{Boolean}} \Bot {\Top \mlrefine z {\\
&\ \gap \ldecl {\mi{ifNat}} {(r.\mi{Unit} \tfun r.\mi{Nat}) \tfun (r.\mi{Unit} \tfun r.\mi{Nat}) \tfun r.\mi{Nat}}\\
&\gap}}\\
&\ \ldecl {\mi{false}} {{r.\mi{Unit}} \tfun {r.\mi{Boolean}}}\\
&\ \ldecl {\mi{true}} {{r.\mi{Unit}} \tfun {r.\mi{Boolean}}}\\
&\ \ldots\\
&\ \ldecl {\mi{error}} {{r.\mi{Unit}} \tfun \Bot}\\
&}\mlldefs{\\\displaybreak[3]
&\ \mi{unit}  = \abs x \Top {\new u {\mi{root}.\mi{Unit}} u}\\
%
&\ \mi{false} = \abs u {\mi{root}.\mi{Unit}} {\\
&\ \gap \mlnew {\mi{ff}} {\mi{root}.\mi{Boolean} \mlldefs{\\
&\ \gap\gap {\mi{ifNat}} = \abs t {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Nat}} {\\&\gap\gap\gap\abs e {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Nat}}\\&\gap\gap\gap\app e {\mi{root}.\mi{unit}}}\\
&\ \gap}}{
\ \gap \mi{ff}}
&}\\
%
&\ \mi{true} = \ldots\\
%
&\ \mi{error} = \abs u {\mi{root}.\mi{Unit}} {\app {\mi{root}.\mi{error}} u}\\
&}}{
\ldots
}
\end{align*}

\begin{align*}
&\mlnew {\mi{genLists}} {\Top \mlrefine g {\Ldecl {\mi{ListPackage}} \Bot {\Top \mlrefine p {\\
&\ \Ldecl {\mi{Elem}} \Bot \Top\\
&\ \Ldecl {\mi{ListOfElement}} {g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}} {\\&\gap\gap\gap\gap g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}}\\
&\ \Ldecl {\mi{List}} \Bot {\Top \mlrefine z {\\
&\ \gap \ldecl {\mi{isEmpty}} {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Boolean}}\\
&\ \gap \ldecl {\mi{head}} {\mi{root}.\mi{Unit} \tfun g.\mi{Elem}}\\
&\ \gap \ldecl {\mi{tail}} {\mi{root}.\mi{Unit} \tfun g.\mi{ListOfElem}}\\
&\gap}}\\
&\ \ldecl {\mi{nil}} {\mi{root}.\mi{Unit} \tfun g.\mi{ListOfElem}}\\
&\ \ldecl {\mi{cons}} {g.\mi{Elem} \tfun g.\mi{ListOfElem}}\\
&}}}}{
\mlnew {\mi{natLists}} {{\mi{genLists}.\mi{ListPacakge}} \mlrefine p { \Ldecl {\mi{Elem}} {\mi{Nat}} {\mi{Nat}} }\mlldefs{\\
&\ {\mi{nil}} = \ldots\\
&\ {\mi{cons}} = \ldots\\
&}}}{
\ldots
}
\end{align*}
